---
title: "CTT ICCs"
format: dashboard
server: shiny
---

## {.sidebar}

Your data file should be structured such that each column represents an item and each row represents a respondent. We assume your data file **only** contains binary responses (scored 1 and 0 -- NAs are permitted).

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
```

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

The Item Characteristic Curves are replotted each time you select or de-select an item. User may therefore be interested in gaining visual feedback of item functioning within unique sets of items. When developing subtests this tool should be considered benefitial for making item retention or deletion decisions at the subtest level.

```{r}
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})
```
